Variational Monte Carlo on bosonic systems

### 2018-03-21 project_1/article/article.tex

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}

@@

        INSERT PSEUDO-CODE DESCRIPTION OF ALGORITHM?

>>>>

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}

@@

        % Flow chart for description of automatic blocking algorithm
		\begin{figure}
			\centering

        		% Defining blocks of flowchart
        		\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
   			 	text width=5em, text badly centered, node distance=3cm, inner sep=0pt]
			\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    				text width=10em, text centered, rounded corners, minimum height=4em]
			\tikzstyle{line} = [draw, -latex']

    			% Actual figure
    			\begin{tikzpicture}[node distance = 2.2cm, auto]

    				% Nodes
    				\node [block] (init) {Start with $\mathbf{X}_i$, $i=0$};
    				\node [block, below of=init] (variance) {Compute variance and autocovariance of $\mathbf{X}_i$, $s_i$ and $\gamma_i$};
    				\node [block, below of=variance] (transform) 
    					{Transform data $(\mathbf{X}_{i+1})_k = \frac{1}{2}\left((\mathbf{X})_i)_{2k-1} + (\mathbf{X}_i)_{2k} \right)$};
    				\node [block, right=1.5cm of transform] (i+1) {Next iteration: $i = i + 1$.} ;
    				\node [decision, below of = transform] (x_size) {Length of $\mathbf{X}_{i + 1} \geq 2$ ? }; 
    				\node [block, below of=x_size] (m_test) {Compute test statistic $M_j$};
    				\node [block, below of=m_test] (magic_numbers) {Find first $k$ so that $M_k \leq q_{d-k}(1-\alpha)$};
    				\node [block, below of=magic_numbers] (return) {Return $s_k^2/n_k$};

    				% Edges
    				\path [line] (init) -- (variance);
    				\path [line] (variance) -- (transform);
    				\path [line] (transform) -- (x_size);
    					\path [line] (x_size) -| node [near start] {yes} (i+1);
    					\path [line] (i+1) |- (variance);
    				\path [line] (x_size) -- node [near start] {no} (m_test);
    				\path [line] (m_test) -- (magic_numbers);
    				\path [line] (magic_numbers) -- (return);
    			\end{tikzpicture}
    			\caption{Flow chart, blocking algorithm.}
		\end{figure}
